### 2023-05-29 paper/Chapters/Chapter1.tex
Updates

This paper has the following structure: in \cref{cha:related_work}, we will describe
various subtopics of the camera calibration, and outline the current state-of-the-art solutions.
In \cref{cha:background}, we will describe the key concepts of camera
calibration. Also, there we provide additional details on the underlying math,
for example, the derivation of the division model inversion. In
\cref{cha:approach}, we will describe the steps of the proposed method in
detail, including feature detection, initial camera calibration, camera
parameters estimation via minimization of the reprojection error, and the
process of searching and filtering the previously undetected features. In
\cref{cha:experiments}, we will describe the metrics we used, provide details about
the datasets, show the results of each of the algorithm's steps, and evaluate it
on multiple metrics. Finally, in \cref{cha:conclusions}, we will summarize the
results and outline future work.

>>>>

This paper has the following structure: in \cref{cha:related_work}, we will describe
subtopics of the camera calibration, and outline the current state-of-the-art solutions.
In \cref{cha:background}, we will describe the key concepts of camera
calibration. Also, there we provide additional details on the underlying math,
for example, the derivation of the division model inversion. In
\cref{cha:approach}, we will describe the steps of the proposed method in
detail, including feature detection, initial camera calibration, camera
parameters estimation via minimization of the reprojection error, and the
process of searching and filtering the previously undetected features. In
\cref{cha:experiments}, we will describe the metrics we used, provide details about
the datasets, show the results of each of the algorithm's steps, and evaluate it
on multiple metrics. Finally, in \cref{cha:conclusions}, we will summarize the
results and outline future work.

### 2023-05-29 paper/Chapters/Chapter2.tex
Updates

Later, ArUco
~\citep{garrido-juradoAutomaticGenerationDetection2014} (\cref{fig:gboriginal}) and
AprilTag~\citep{olsonAprilTagRobustFlexible2011} (\cref{fig:apriltag})
allowed detecting the
orientation of the pattern, as well as uniquely identifying each located pattern
even under occlusion. Based on ArUco,
ChArUcO~\citep{OpenCVCameraCalibration} (\cref{fig:charuco}) was
proposed as more robust.

@@

The choice of the camera model depends on the camera's physical properties
and the accuracy required. Usually, the parametric models are simpler to use, as
they have only a few parameters and deliver good accuracy.
The most common are the Double Sphere
model~\citep{usenkoDoubleSphereCamera2018}, the Kannala-Brandt
model~\citep{kannalaGenericCameraModel2006}, and the Field-of-View
model~\citep{devernayStraightLinesHave2001}.
In the ill-posed problem of camera calibration, the common choice
of the camera model is the division
model~\citep{fitzgibbonSimultaneousLinearEstimation2001}.
However, \cite{schopsWhyHaving102020} shows that they tend to have
significantly higher errors than the non-parametric (general) models.
The \cite{lochmanBabelCalibUniversalApproach2021} suggested a framework for
converting the parameters of a powerful back-projection
\cite{zhangFlexibleNewTechnique2000} model to recover different models' parameters.

@@

% Camera calibration is a crucial step for many computer vision tasks,
% hence many methods were proposed to solve this problem (e.g.,
% ~\cite{brownCloseRangeCameraCalibration1971},
% ~\cite{heikkilaFourstepCameraCalibration1997},
% ~\cite{fitzgibbonSimultaneousLinearEstimation2001},
% ~\cite{sturmGenericConceptCamera2004},
% ~\cite{clausRationalFunctionLens2005},
% ~\cite{meiSingleViewPoint2007},
% ~\cite{ramalingamUnifyingModelCamera2017}).

Nevertheless, camera calibration is still an open problem; recently,
multiple new approaches have arisen.
\cite{scaramuzzaToolboxEasilyCalibrating2006} proposed an automatic algorithm
for camera calibration, which did not use any model of the specific omnidirectional
sensor.
\cite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
to camera calibration, with a separate step of converting between camera models.
\cite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
Recently, on \citedate{duisterhofTartanCalibIterativeWideAngle2022},
\cite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
approach to camera calibration, which outperforms the previous state-of-the-art
approaches for wide-angle cameras.

@@

Because of that, other methods were proposed, such as
\cite{fuersattelOCPADOccludedCheckerboard2016} and
\cite{geigerAutomaticCameraRange2012}. Those methods can detect the board and
associate the corners with the borders' corners under
the partial occlusion and do not require prior knowledge of the board's geometry.

\cite{chenNewSubPixelDetector2005} proposed using Hessian to find pixel
positions of the corners.

>>>>

Later, ArUco
~\citep{garrido-juradoAutomaticGenerationDetection2014} (\cref{fig:gboriginal}) and
AprilTag~\citep{olsonAprilTagRobustFlexible2011} (\cref{fig:apriltag})
allowed detecting the
orientation of the pattern, as well as uniquely identifying each located pattern
even under occlusion. Later, based on ArUco pattern,
ChArUcO~\citep{OpenCVCameraCalibration} (\cref{fig:charuco}) was
proposed as more robust.

@@

The choice of the camera model depends on the camera's physical properties
and the accuracy required. Usually, the parametric models are simpler to use, as
they have only a few parameters and deliver good accuracy.
The most common are the Double Sphere
model~\citep{usenkoDoubleSphereCamera2018}, the Kannala-Brandt
model~\citep{kannalaGenericCameraModel2006}, and the Field-of-View
model~\citep{devernayStraightLinesHave2001}.
In the ill-posed problem of camera calibration, the common choice
of the camera model is the division
model~\citep{fitzgibbonSimultaneousLinearEstimation2001}. This model is
discussed in details in \cref{sub:distortion}.
However, \cite{schopsWhyHaving102020} shows that they tend to have
significantly higher errors than the non-parametric (general) models.
The \cite{lochmanBabelCalibUniversalApproach2021} suggested a framework for
converting the parameters of a powerful back-projection
\cite{zhangFlexibleNewTechnique2000} model to recover different models' parameters.

@@

% Camera calibration is a crucial step for many computer vision tasks,
% hence many methods were proposed to solve this problem (e.g.,
% ~\cite{brownCloseRangeCameraCalibration1971,
% heikkilaFourstepCameraCalibration1997,
% fitzgibbonSimultaneousLinearEstimation2001,
% sturmGenericConceptCamera2004,
% clausRationalFunctionLens2005,
% meiSingleViewPoint2007,
% ramalingamUnifyingModelCamera2017}).

Nevertheless, camera calibration is still an open problem; recently,
multiple new approaches have arisen.
\cite{scaramuzzaToolboxEasilyCalibrating2006} proposed an automatic algorithm
for camera calibration, which did not use any model of the specific omnidirectional
sensor. Is is described in details in \cref{sub:initial_approximation}.
\cite{lochmanBabelCalibUniversalApproach2021} suggest a universal approach
to camera calibration, with a separate step of converting between camera models.
\cite{huDeepChArUcoDark2019} used deep learning to detect ChArUcO boards.
Recently, on \citedate{duisterhofTartanCalibIterativeWideAngle2022},
\cite{duisterhofTartanCalibIterativeWideAngle2022} introduced the iterative
approach to camera calibration, which outperforms the previous state-of-the-art
approaches for wide-angle cameras.

@@

Because of that, other methods were proposed, such as
\cite{fuersattelOCPADOccludedCheckerboard2016} and
\cite{geigerAutomaticCameraRange2012} (\cref{sub:corner_detection}). Those methods can detect the board and
associate the corners with the borders' corners under
the partial occlusion and do not require prior knowledge of the board's geometry.

\cite{chenNewSubPixelDetector2005} (\cref{sub:corner_detection}) proposed using Hessian to find pixel
positions of the corners.

### 2023-05-29 paper/Chapters/Chapter5.tex
Final updates
Updates

As currently the algorithm only supports processing a single checkerboard, we
cannot compare to \cite{duisterhofTartanCalibIterativeWideAngle2022}, which uses
AprilTags, nor to the \cite{lochmanBabelCalibUniversalApproach2021}, who
provides the detected corners for all of the boards.
\todo{Should I maybe tell less about it?}

@@

\textcite{lochmanBabelCalibUniversalApproach2021} collected a wide number of
datasets, typically used in the field for the benchmarking of the camera
calibration. They're provided in a Deltille \cite{DeltilleDetector2023} format,
and are well documented:

@@

\section{Camera calibration}\label{sec:camera_calibration}

@@

\section{Additional features detection}\label{sec:additional_features_detection}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\linewidth}
		\begin{tikzpicture}
			\begin{axis}[
					ybar interval,
					ymin=0,
					ylabel={Frequency},
					xlabel={Value},
					height=0.5\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					title={Histogram of the points before refinement}
				]
				\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/pruned_number_of_features.txt};
			\end{axis}
		\end{tikzpicture}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\linewidth}
		% \centering
		\begin{tikzpicture}
			\begin{axis}[
					ybar interval,
					ymin=0,
					ylabel={Frequency},
					xlabel={Value},
					height=0.5\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					title={Histogram of the points after refinement}
				]
				\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/recovered_pruned_number_of_features.txt};
			\end{axis}
		\end{tikzpicture}
	\end{subfigure}
	\begin{subfigure}[h]{\linewidth}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{subfigure}
	\hfill
	\caption{Feature refinement on the board with 80\% of the points}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\linewidth}
		\begin{tikzpicture}
			\begin{axis}[
					ybar interval,
					ymin=0,
					ylabel={Frequency},
					xlabel={Value},
					height=0.5\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					title={Histogram of the points before the refinement}
				]
				\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/occluded_number_of_features.txt};
			\end{axis}
		\end{tikzpicture}
		\caption{}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\linewidth}
		% \centering
		\begin{tikzpicture}
			\begin{axis}[
					ybar interval,
					ymin=0,
					ylabel={Frequency},
					xlabel={Value},
					height=0.5\linewidth,
					width=\linewidth,
					ticklabel style = {font=\tiny},
					title={Histogram of the points after the refinement}
				]
				\addplot+ [hist={data min=0,data max=500,bins=20}] table [y index=0]
					% \addplot+ [hist={bins=30}] table [y index=0]
					{data/recovered_occluded_number_of_features.txt};
			\end{axis}
		\end{tikzpicture}
	\end{subfigure}
	\begin{subfigure}[h]{\linewidth}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{subfigure}
	\hfill
	\caption{Feature refinement on the board with partial board occlusion}
\end{figure}

@@

\begin{minipage}[t]{0.3\linewidth}
	Lastly, we recovered the points that were not detected by the initial feature
	detector.
	From a visual inspection, most of the points were recovered correctly
	\cref{fig:recovered_good_points}.
	On the top image, for example, there are green points close to the edge.
	Those corners weren't detected initially due to high distortion. On the bottom
	image, the algorithm found another row of corners, which weren't detected previously.
\end{minipage}
\hfill
\begin{minipage}[t]{0.6\linewidth}
	\includegraphics[width=\linewidth]{refined_corners1.png}
	\includegraphics[width=\linewidth]{refined_corners2.png}

	\captionof{figure}{Recovered points
		(\textcolor[HTML]{1f77b4}{unchanged}
		\textcolor[HTML]{ff7f0e}{filtered out}
		\textcolor[HTML]{2ca02c}{new corner}
		\textcolor[HTML]{d62728}{out of image})}
	\label{fig:recovered_good_points}
\end{minipage}

\begin{minipage}[t]{0.3\linewidth}
	However,
	because of the occlusions, or similar to the board patterns in the background,
	there were false positives \cref{fig:recovered_bad_points}. Many images didn't
	have undetected corners, hence it's hard to make a general statement about the
	performance of the feature detector solely based on this experiment
	\cref{fig:recovered_points_histogram}.
\end{minipage}
\hfill
\begin{minipage}[t]{0.6\linewidth}
	\includegraphics[width=\linewidth]{refined_corners_bad.png}
	\captionof{figure}{Occlusion on the board with distinct features}
	\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
	\captionof{figure}{Similar pattern to the board in the background}
	\label{fig:recovered_bad_points}
\end{minipage}

\begin{figure}[h]
	\begin{tikzpicture}
		\begin{axis}			[
				ymode=log,
				ybar interval,
				ymin=0,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=100,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/number_of_refined_points.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Histogram of the newly recovered features}
	\label{fig:recovered_points_histogram}
\end{figure}

>>>>

As currently the algorithm only supports processing a single checkerboard, we
cannot compare to \cite{duisterhofTartanCalibIterativeWideAngle2022}, which uses
AprilTags, nor to the \cite{lochmanBabelCalibUniversalApproach2021}, who
provides the detected corners for all of the boards.

@@

\textcite{lochmanBabelCalibUniversalApproach2021} collected a wide number of
datasets, typically used in the field for the benchmarking of the camera
calibration. They're provided in a Deltille \cite{DeltilleDetector2023} format,
and are well documented.

@@

\section{Camera calibration}\label{sec:camera_calibration_exp}

@@

\section{Additional features detection}\label{sec:additional_features_detection_exp}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\linewidth}
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						ybar interval,
						ymin=0,
						ylabel={Frequency},
						xlabel={Value},
						height=0.5\linewidth,
						width=\linewidth,
						ticklabel style = {font=\tiny},
						title={Histogram of points before refinement}
					]
					\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
						% \addplot+ [hist={bins=30}] table [y index=0]
						{data/pruned_number_of_features.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\linewidth}
		% \centering
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						ybar interval,
						ymin=0,
						ylabel={Frequency},
						xlabel={Value},
						height=0.5\linewidth,
						width=\linewidth,
						ticklabel style = {font=\tiny},
						title={Histogram of points after refinement}
					]
					\addplot+ [hist={data min=0,data max=600,bins=10}] table [y index=0]
						% \addplot+ [hist={bins=30}] table [y index=0]
						{data/recovered_pruned_number_of_features.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{subfigure}
	\begin{subfigure}[h]{\linewidth}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{subfigure}
	\hfill
	\caption{Feature refinement on the board with 80\% of the points}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.45\linewidth}
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						ybar interval,
						ymin=0,
						ylabel={Frequency},
						xlabel={Value},
						height=0.5\linewidth,
						width=\linewidth,
						ticklabel style = {font=\tiny},
						title={Histogram of points before refinement}
					]
					\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
						% \addplot+ [hist={bins=30}] table [y index=0]
						{data/occluded_number_of_features.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{subfigure}
	\hfill
	\begin{subfigure}[h]{0.45\linewidth}
		% \centering
		\resizebox{\linewidth}{!}{
			\begin{tikzpicture}
				\begin{axis}[
						ybar interval,
						ymin=0,
						ylabel={Frequency},
						xlabel={Value},
						height=0.5\linewidth,
						width=\linewidth,
						ticklabel style = {font=\tiny},
						title={Histogram of points after refinement}
					]
					\addplot+ [hist={data min=0,data max=500,bins=10}] table [y index=0]
						% \addplot+ [hist={bins=30}] table [y index=0]
						{data/recovered_occluded_number_of_features.txt};
				\end{axis}
			\end{tikzpicture}
		}
	\end{subfigure}
	\begin{subfigure}[h]{\linewidth}
		\centering
		\includegraphics[width=0.7\linewidth]{refined_pruned_corners.png}
		\caption{Recovered pruned points
			(\textcolor[HTML]{1f77b4}{unchanged}
			\textcolor[HTML]{ff7f0e}{filtered out}
			\textcolor[HTML]{2ca02c}{new corner}
			\textcolor[HTML]{d62728}{out of image})}
	\end{subfigure}
	\hfill
	\caption{Feature refinement on the board with partial board occlusion}
\end{figure}

@@

Lastly, we recovered the points that were not detected by the initial feature
detector.
From a visual inspection, most of the points were recovered correctly
\cref{fig:recovered_good_points}.
On the top image, for example, there are green points close to the edge.
Those corners weren't detected initially due to high distortion. On the bottom
image, the algorithm found another row of corners, which weren't detected previously.

% \begin{minipage}[t]{0.80\linewidth}
\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\linewidth]{refined_corners1.png}
	\includegraphics[width=0.75\linewidth]{refined_corners2.png}

	\caption{Recovered points
		(\textcolor[HTML]{1f77b4}{unchanged}
		\textcolor[HTML]{ff7f0e}{filtered out}
		\textcolor[HTML]{2ca02c}{new corner}
		\textcolor[HTML]{d62728}{out of image})}
	\label{fig:recovered_good_points}
\end{figure}
% \end{minipage}

\newpage
However,
because of the occlusions, or similar to the board patterns in the background,
there were false positives (\cref{fig:recovered_bad_points}). Many images didn't
have undetected corners, hence it's hard to make a general statement about the
performance of the feature detector solely based on this experiment
(\cref{fig:recovered_points_histogram}.)

\begin{figure}[h]
	\centering
	\begin{subfigure}[h]{0.6\linewidth}
		\includegraphics[width=\linewidth]{refined_corners_bad.png}
		\caption{Occlusion on the board with distinct features}
	\end{subfigure}
	\begin{subfigure}[h]{0.6\linewidth}
		\includegraphics[width=\linewidth]{refined_corners_bad_bad.png}
		\caption{Similar pattern to the board in the background}
	\end{subfigure}
	\label{fig:recovered_bad_points}
\end{figure}

\begin{figure}[h!]
	\begin{tikzpicture}
		\begin{axis}			[
				ymode=log,
				ybar interval,
				ylabel={Frequency},
				xlabel={Value},
				height=0.3\linewidth,
				width=\linewidth,
				ticklabel style = {font=\tiny},
				% title={Initial calibration}
			]
			\addplot+ [hist={data min=0,data max=50,bins=20}] table [y index=0]
				% \addplot+ [hist={bins=30}] table [y index=0]
				{data/number_of_refined_points.txt};
		\end{axis}
	\end{tikzpicture}
	\caption{Histogram of the newly recovered features}
	\label{fig:recovered_points_histogram}
\end{figure}

### 2023-05-29 paper/paper.tex
Final updates
Updates

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
openany
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\usepackage[textwidth=20mm]{todonotes}
\setlength{\marginparwidth}{2.5cm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{xfrac}
\usepackage{multicol}
\usepackage{float}
\usepackage{cases}
\usepackage{pgfplots}
\usepackage{pgf-pie}
\usetikzlibrary{spy,arrows}
\graphicspath{ {images/} }

@@

\thesistitle{Corner localization and camera calibration from imaged lattices} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. James \textsc{Pritts}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Master of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Andrii \textsc{Stadnik}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Data Science} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.ucu.edu.ua}{Ukrainian Catholic University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
% \department{\href{http://department.university.com}{Faculty of Applied Sciences}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
% \group{\href{http://researchgroup.university.com}{Department of Computer Sciences}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
% \faculty{\href{http://faculty.university.com}{}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
\department{Faculty of Applied Sciences} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{Department of Computer Sciences} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

@@

\begin{document}
\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages

@@

		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushleft} \large
				\emph{Author:}\\
				% \href{http://www.johnsmith.com}{\authorname} % Author name - remove the \href bracket to remove the link
				\authorname % Author name - remove the \href bracket to remove the link
			\end{flushleft}
		\end{minipage}
		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushright} \large
				\emph{Supervisor:} \\
				\href{https://prittjam.github.io/}{\supname} % Supervisor name - remove the \href bracket to remove the link  
			\end{flushright}
		\end{minipage}\\[3cm]

@@

		\vfill
		\includegraphics[height=3cm]{UCU-Apps 2022.png} % University/department logo - uncomment to place it

		\vfill
		{\large Lviv 2022}\\[4cm] % Date

@@

	Current state-of-the-art techniques occasionally fail to accurately estimate
	the camera parameters for wide-angle lenses, as most of the algorithms assume
	lenses with medium to small distortion. Partially it occurs due to extreme
	distortion at the edges of the image, which poses additional challenges to
	feature detection algorithms. We propose a novel approach for detecting
	additional features on the imaged calibration pattern using intermediate
	camera calibration. Utilizing the prior information about the calibration
	pattern's geometry, we can estimate the possible positions of the previously
	undetected features. Those features are filtered using the binary classifier,
	and the remaining ones are used to further constrain the camera calibration.
	The proposed method consists of three key steps: \((1)\) feature
	detection and estimation of the lattice geometry, \((2)\) initial camera
	calibration by solving the two-step linear minimization problem, and \((3)\)
	estimation of the possible positions of the undetected features by projecting the
	imputed and extended lattice geometry onto the image plane, and filtering them
	using the binary classifier.

  The code for this paper is available at
  \url{https://github.com/anstadnik/camera_calibration}.

@@

	% \noindent If you was supported with the scholarship, please thank to your donor organization or a person who supported you.
\end{acknowledgements}

@@

% \begin{symbols}{lll} % Include a list of Symbols (a three column table)
%
% 	$a$ & distance & \si{\meter} \\
% 	$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
% 	%Symbol & Name & Unit \\
%
% 	\addlinespace % Gap to separate the Roman symbols from the Greek
%
% 	$\omega$ & angular frequency & \si{\radian} \\
%
% \end{symbols}

@@

\pagestyle{thesis} % Return the page headers back to the "thesis" style

\listoftodos{1}
\todo{Remove list of todos}

@@

\printbibliography[heading=bibintoc]

>>>>

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two sides (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgments pages to match the default layout
openany
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\setlength{\marginparwidth}{2.5cm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{xfrac}
\usepackage{multicol}
\usepackage{float}
\usepackage{cases}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usepackage{pgf-pie}
\usepackage{microtype}
\usetikzlibrary{spy,arrows}
\graphicspath{ {images/} }

@@

\thesistitle{Corner localization and camera calibration from imaged lattices} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Dr. James \textsc{Pritts}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Master of Science} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Andrii \textsc{Stadnik}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Data Science} % Your subject area, is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://www.ucu.edu.ua}{Ukrainian Catholic University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
% \department{\href{http://department.university.com}{Faculty of Applied Sciences}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
% \group{\href{http://researchgroup.university.com}{Department of Computer Sciences}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
% \faculty{\href{http://faculty.university.com}{}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
\department{Faculty of Applied Sciences} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{Department of Computer Sciences} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

@@

\begin{document}
\frontmatter % Use Roman page numbering style (i, ii, iii, iv...) for the pre-content pages

@@

		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushleft} \large
				\emph{Author:}\\
				\href{https://www.linkedin.com/in/anstadnik/}{\authorname} % Author name - remove the \href bracket to remove the link
				% \authorname % Author name - remove the \href bracket to remove the link
			\end{flushleft}
		\end{minipage}
		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushright} \large
				\emph{Supervisor:} \\
				\href{https://prittjam.github.io/}{\supname} % Supervisor name - remove the \href bracket to remove the link  
			\end{flushright}
		\end{minipage}\\[3cm]

@@

		\vfill
		\includegraphics[height=3cm]{UCU-Apps2022_.png} % University/department logo - uncomment to place it

		\vfill
		{\large Lviv 2023}\\[4cm] % Date

@@

	% Current state-of-the-art techniques occasionally fail to accurately estimate
	% the camera parameters for wide-angle lenses, as most of the algorithms assume
	% lenses with medium to small distortion. Partially it occurs due to extreme
	% distortion at the edges of the image, which poses additional challenges to
	% feature detection algorithms. We propose a novel approach to detecting
	% additional features on the imaged calibration pattern using intermediate
	% camera calibration. Utilizing the prior information about the calibration
	% pattern's geometry, we can estimate the possible positions of the previously
	% undetected features. Those features are filtered using the binary classifier,
	% and the remaining ones are used to further constrain the camera calibration.
	% The proposed method consists of three key steps: \((1)\) feature
	% detection and estimation of the lattice geometry, \((2)\) initial camera
	% calibration by solving the two-step linear minimization problem, and \((3)\)
	% estimation of the possible positions of the undetected features by projecting the
	% imputed and extended lattice geometry onto the image plane, and filtered them
	% using the binary classifier.

  This thesis proposes a model-based approach to improve the detection of
  calibration board fiducials from calibration imagery taken by wide-angle or
  fisheye lenses. From a single image, we estimate the camera model and project
  the calibration board into the image to guide the search for missed detections
  and reject spurious detections. In addition, we propose a classifier to label
  ambiguous detections that are geometrically plausible given the estimated
  camera model and imaged board. The proposed method addresses shortcomings of
  the state-of-the-art, which struggle to reliably detect board fiducials at the
  extents of the image, where the lens distortion is most observable. The
  proposed method recovers additional corners that can be used to place
  additional constraints on the non-convex camera calibration problem, which
  improves the likelihood of convergence to a global minimum.

  The code for this paper is available on GitHub
  \footnote{\url{https://github.com/anstadnik/camera_calibration}}.

@@

	% \noindent If you were supported with the scholarship, please thank your donor organization or a person who supported you.
\end{acknowledgements}

@@

% \begin{symbols}{lll} % Include a list of Symbols (a three-column table)
%
% 	$a$ & distance & \si{\meter} \\
% 	$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
% 	%Symbol & Name & Unit \\
%
% 	\addlinespace % Gap to separate the Roman symbols from the Greek
%
% 	$\omega$ & angular frequency & \si{\radian} \\
%
% \end{symbols}

@@

\pagestyle{thesis} % Return the page headers to the "thesis" style

@@

% \emergencystretch=1em
% \Urlmuskip=0mu plus 1mu\relax

\setcounter{biburllcpenalty}{7000}
\setcounter{biburlucpenalty}{8000}
\printbibliography[heading=bibintoc]
